SHARP - II: Revealing a bias in observational measurements of dark matter substructure with gravitational lens flux ratios

### 2015-11-17 papers/B1555_EdgeOn/B1555_letter.tex
fix typo in the text

B1555+375 was also observed with the {\it HST} in three broad bands.  The optical data were obtained with the Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands (GO-8804; PI: Falco), while the Near Infrared Multi-Object Spectrograph (NICMOS) was used to observe the system in the F160W band (GO-9744; PI: Kochanek).  The NICMOS observations were obtained with the NIC2 camera.  We reduced all of the archival \textit{HST} data with the standard {\sc multidrizzle} pipeline, producing final drizzled images with pixel-sizes of 50~mas. The reduced images are also shown in Fig.~\ref{fig:multiband}. The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image

@@

\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account 
 (e.g., \citet{Xu15}). This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines (e.g., \citet{N14}). Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components. Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyways; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}

>>>>

B1555+375 was also observed with the {\it HST} in three broad bands.  The optical data were obtained with the Wide-Field Planetary Camera 2 (WFPC2) in the F555W and F814W bands (GO-8804; PI: Falco), while the Near Infrared Multi-Object Spectrograph (NICMOS) was used to observe the system in the F160W band (GO-9744; PI: Kochanek).  The NICMOS observations were obtained with the NIC2 camera.  We reduced all of the archival \textit{HST} data with the standard {\sc multidrizzle} pipeline, producing final drizzled images with pixel-sizes of 50~mas. The reduced images are also shown in Fig.~\ref{fig:multiband}. The lens and the lensed images are not detected at high significance in the optical bands, but are clearly seen in the NICMOS F160W image.

@@

\textbf{ Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies. Before concluding that the flux-ratio anomalies in any given lens system are the result of dark matter substructure, then, it is critical that other possible sources of significant curvature in the lensing potential (i.e., `sharp' mass features such as edge-on disks or even massive luminous satellites) are taken into account 
 (e.g., \citet{Xu15}). This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines (e.g., \citet{N14}). Near-infrared AO imaging of other lenses in the SHARP sample shows that B1555+375 is not the only system having a significant disc component detection in the lensing galaxy; these gravitational lenses will be investigated in future work, but the images alone suggest that other systems may have similar links between flux-ratio anomalies and disc components. Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems (and the presence of a disc-like component may not resolve the anomaly anyway; \citet{evans03}), indicating that these systems are still useful for probing the dark matter substructure mass function.}
